### 2021-03-08 research project/sections/Background.tex
rp work

Since the equation for the area of a polygon is defined as $A = \frac{p \cdot a}{2}$,
where $p$ is the perimeter of the polygon and $a$ is the apothem\footnote{apothem: the segment 
from the center of a polygon to the midpoint of one of its sides, here $OH$ for the $n$-gon and 
$OH'$ for the $2n$-gon}, in this case $BD \cdot n$
and $OH$ respectively, let $A_{n}$ equal the area of
the polygon with $n$ sides (displayed in \textcolor{green}{green} in Figure 2) such that: \\
$A_{n} = \frac{OH \cdot BD \cdot n}{2}$ \\
$A_{n} = \frac{R \cos{\alpha} \cdot 2 R \sin{\alpha} \cdot n}{2} = n R^2 \sin{\alpha} \cos{\alpha}$

@@

It can be then written that, through a new variable $P$, \\
$P = \frac{A_{n}}{A_{2n}} \frac{A_{2n}}{A_{4n}} \frac{A_{4n}}{A_{8n}} \dots \frac{A_{(k-2)n}}{A_{kn}} \frac{A_{kn}}{A}$ \\
where $A$ is the area of the circle of radius $R$
in \ref{fig:image1}.

So $P = \frac{A_{n}}{A}$, since the values $A_{kn}$ cancel, and
so it is true that $P = \frac{A_{n}}{A} \Leftrightarrow A = \frac{A_{n}}{P}$. The
value of $R = 1$ in this case, and since the area of a circle is defined
by $A = \pi R^2$, therefore: \\
$\pi = \frac{A_{n}}{P}$ \\
By definition, we can say that as the value $k$ approaches infinity, the area of the $kn$-gon
approaches that of a circle, and therefore, the value of $\pi$.

@@

Where the value of $A_{n}$ is the area of the first polygon, with $n=4$ sides, and as such
$A_{n} = 4 \sin{45} \cos{45} = 2$. We can define: \\
$U_{0} = \cos{a} = \cos{45} = \frac{1}{\sqrt{2}}$ \\
$U_{1} = cos{\frac{\alpha}{2}}$ \\
Which we can, through the trigonometric identity
$\cos^2{\theta} = \frac{1}{2} + \frac{1}{2} \cos{2\theta}$, simplify as
$U_{1} = \sqrt{\frac{1}{2} + \frac{1}{2} U_{0}}$ \\
So it can be said that $U_{n} = \sqrt{\frac{1}{2} + \frac{1}{2} U_{n - 1}}$, which leads to
a fully defined expression for the value of pi, using an infinite product:

>>>>

Since the equation for the area of a polygon is defined as $A = \frac{p \cdot a}{2}$,
where $p$ is the perimeter of the polygon and $a$ is the apothem\footnote{apothem: the segment from the center of a polygon to the midpoint of one of its sides, here $OH$ for the $n$-gon and $OH'$ for the $2n$-gon}, in this case $BD \cdot n$ and $OH$ respectively, let $A_{n}$ equal the area of the polygon with $n$ sides (displayed in \textcolor{green}{green} in Figure 2) such that:

$A_{n} = \frac{OH \cdot BD \cdot n}{2}$

$A_{n} = \frac{R \cos{\alpha} \cdot 2 R \sin{\alpha} \cdot n}{2} = n R^2 \sin{\alpha} \cos{\alpha}$

@@

It can be then written that, through a new variable $P$,

$P = \frac{A_{n}}{A_{2n}} \frac{A_{2n}}{A_{4n}} \frac{A_{4n}}{A_{8n}} \dots \frac{A_{(k-2)n}}{A_{kn}} \frac{A_{kn}}{A}$

where $A$ is the area of the circle of radius $R$ in \ref{fig:image1}.

So $P = \frac{A_{n}}{A}$, since the values $A_{kn}$ cancel, and so it is true that $P = \frac{A_{n}}{A} \Leftrightarrow A = \frac{A_{n}}{P}$. The value of $R = 1$ in this case, and since the area of a circle is defined by $A = \pi R^2$, therefore:

$\pi = \frac{A_{n}}{P}$

By definition, we can say that as the value $k$ approaches infinity, the area of the $kn$-gon approaches that of a circle, and therefore, the value of $\pi$.

@@

Where the value of $A_{n}$ is the area of the first polygon, with $n=4$ sides, and as such
$A_{n} = 4 \sin{45} \cos{45} = 2$. We can define:

$U_{0} = \cos{a} = \cos{45} = \frac{1}{\sqrt{2}}$

$U_{1} = cos{\frac{\alpha}{2}}$

Which we can, through the trigonometric identity
$\cos^2{\theta} = \frac{1}{2} + \frac{1}{2} \cos{2\theta}$, simplify as

$U_{1} = \sqrt{\frac{1}{2} + \frac{1}{2} U_{0}}$

So it can be said that $U_{n} = \sqrt{\frac{1}{2} + \frac{1}{2} U_{n - 1}}$, which leads to a fully defined expression for the value of pi, using an infinite product:
